\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-04-12 Latex/paper-resum.tex
Stylish 2

\author[1,2]{David Garcia-Lorite\thanks{Corresponding author, \email{dddd@caixabank.es}}}
\author[3]{Ra\'{u}l Merino}

@@

%\TODO{Remove ToC in final version}
%\tableofcontents
%\clearpage
\blfootnote{The authors would like to thank Elisa Al\`os for helpful discussions.}

@@

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E[t_0]. 
\end{equation}
with 
\begin{equation*}
\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{t_0}k_u du \right) \eta(u,x,y).
\end{equation*}
and $\|E\left[t_0\right]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left[t_0\right]\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

\subsection{OIS futures}
In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs. It is common in the market to find two version of these futures, depending on how the fixings of the refrence index are using. Given $t_0 < t_1$, we will define the overnight compounding rate as
\begin{equation*}
R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
\end{equation*}
and the overnight average rate as
\begin{equation*}
R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
\end{equation*}
We observe that both, $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$. Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales:
\begin{align*} 
\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R(t_0,t_1)  \right], \\
\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R_{avg}(t_0,t_1)  \right].
\end{align*}
Before to continue, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
&= \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), %, \quad t \in [0,t_0] \\
%\end{align*}
\intertext{and when $t \in  [t_0, t_1]$, we have}
%\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
 &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois,u} du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
\end{align*}
Then the convexity adjustment for $ R(t_0,t_1)$ is
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
\end{equation}
The second observation is that we have the following equivalence
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
In order, to clarify the convexity expression and the calculations, we will define 
\begin{equation*}
I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
\end{equation*}

\begin{theorem}\label{Th_CA_OIS}[Convexity Adjustment approximation for OIS Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for OIS futures is 
\begin{equation}\label{convexity_ois_future}
\bar{R}(t_0,t_1) = \frac{1}{\delta_{t_0,t_1}}\left(\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)\exp\left(-\frac{1}{2}\int_{t}^{t_1}\Gamma^{2}(s,t_0,t_1) ds\right) - 1\right) + E[t_0],
\end{equation}
and for the average OIS future is
\begin{equation}\label{convexity_avg_ois_future}
\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] }{\delta_{t_0,t_1}} \approx \frac{1}{\delta_{t_0,t_1}}\left(\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left[R(t_0,t_1)\right] \right) - \frac{1}{2}\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds\right)
\end{equation}
where  
\begin{equation}
\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du, 
\end{equation}
and $\|E[t_0]\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E[t_0]\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_OIS_futures}.
\end{proof}

@@

\begin{remark}
We can calculate the convexity adjustment for the case $t_0 < t < t_1$ similarly to when $t < t_0$. For this, we will define
\begin{equation*}
I(t,t_1):=\int_{t}^{t_1} r_s ds
\end{equation*}
and 
\begin{align*}
R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp(\int_{t}^{t_1} r_{ois,s} ds )}{P_{ois}(t_0,t)} - 1\right), \\
R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois,s} ds + \int_{t}^{t_1} r_{ois,s} ds\right).   
\end{align*}
\end{remark}

@@

\subsection{FRAs in arrears}
A FRA in arrears is the most classic example among the products with convexity adjustment. The price is given by 
\begin{equation}\label{FRAinArrear}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left(L_{E}(t_1,t_1,t_2)\right),
\end{equation}
i.e. the cash flow associated to a FRA in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.

\begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for FRAs in Arrears is 
\begin{equation}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) =   \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \bar{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds E(t_1)
\end{equation}
with $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_FRAsinArrears}.
\end{proof}

\begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
We can restrict the model the the Hull-White model with constant parameters. The analytical approximation that we get from \eqref{ca_approximations_fra_arrears} is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \exp(- k(t_1 + u)) -   \exp(- k(t_2 + u)) du 
\end{equation*}
In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$, $k=0.007$.
\begin{figure}[H]
		\begin{center}
		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
		\end{center}
		\caption{Convexity Mc Vs Convexity Malliavin}
		\label{fig:FRA_HW}
\end{figure}
\end{example}

@@

\begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Given
\begin{equation}
M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}
\end{equation}
Then, we have the temporal convexity adjusment for a CMS rate is approximated by
\begin{align} \label{cms_first_order_convexity}
CA_{CMS}(t_p) &\approx \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber \\
&+ E(t_a)
\end{align}
with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_CMS}.
\end{proof}

@@

\subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left((x_t - \bar{x}_{t})^{2}\right)$}\label{estimation_error_l2}
In order to get the order of the aproximation, we will use the ideas of the paper \cite{B-G-M-2008}. Basically, we will define a parametrization of the process $x_{t,\epsilon}$ e $y_{t,\epsilon}$ with $\epsilon \in [0,1]$. The role of $\epsilon$ is only as interpolator parameter between process. We will suppose the next parametrization of the Cheyette model

@@

The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left(y_t\right)= \mathbb{V}ar(x_t)$. Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$. We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}((y_t - \bar{y}_t)^{2})$. We will define the next parametrization for $\nu \in [0,1]$

@@

Then we have that $z^{1}_{u} = \eta(u,x_u,y_u$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore

@@

y_t = \bar{y}_t + E_{y}(t)

@@

\mathbb{E}^{\mathbb{Q}}((E_{y}(t))^{2}) &\leq 4 \mathbb{E}^{\mathbb{Q}}\left(\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right) ^{2}\nonumber \\ 
&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du = M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left( \|(x_u, y_u)\|^{2}\right) du

@@

The next step is to estimate $\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2})$. From the definition of $x_t$, we have that

@@

x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u. 

@@

In order, to find a expansion of $\eta(t,x_u,y_u)$ centrered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then

@@

\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu

@@

We will define $E_{x}(u) = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}(u) d\nu$. Then we have the next representation of $x_t$

@@

x_t = \bar{x}_t + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u.

@@

 \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}((E_{y}(u))^{2})   

@@

 \mathbb{E}^{\mathbb{Q}}((E_x(u))^{2}) \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left( \|(x_s, y_s)\|^{2}\right) ds

@@

\mathbb{E}^{\mathbb{Q}}((x_t - \bar{x}_t)^{2}) & \leq 2 \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right)^2 + \mathbb{E}^{\mathbb{Q}}\left( \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right)^{2} \\

>>>>

\author[1,2]{David Garcia-Lorite\thanks{Corresponding author, \email{david.garcia.lorite@gmail.com}}}
\author[3]{Ra\'{u}l Merino}

@@

%\TODO{Remove ToC in final version}
%\tableofcontents
%\clearpage
\blfootnote{The authors would like to thank Elisa Al\`os and Josep Vives for helpful discussions.}

@@

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2)  - G(t_0,t_1) \right) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0). 
\end{equation}
with 
\begin{equation*}
\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{t_0}k_u du \right) \eta(u,x,y).
\end{equation*}
and $\|E\left(t_0\right)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E\left(t_0\right)\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

\subsection{OIS futures}
In this section, we will derive the convexity adjustment for short-term interest rate swap, also known as STIRs. It is common in the market to find two version of these futures, depending on how the fixings of the reference index are using. Given $t_0 < t_1$, we will define the overnight compounding rate as
\begin{equation*}
R(t_0,t_1) :=\frac{1}{\delta_{t_0,t_1}} \left(\exp\left(\int_{t_0}^{t_1}r_{ois,u} du \right) - 1\right)
\end{equation*}
and the overnight average rate as
\begin{equation*}
R_{avg}(t_0,t_1) := \frac{1}{\delta_{t_0,t_1}}\int_{t_0}^{t_1}r_{ois,u} du.
\end{equation*}
We observe that both, $R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$  are not predictable and are only observable in $t_1$. However, 
$R(\cdot,t_0,t_1)$ and $R_{avg}(\cdot,t_0,t_1)$ are flows that will be payed in $t_1$. Therefore, we can consider that the expected value under the measure $\mathbb{Q}$ is observable during entire period $[t_0, t_1]$. Let us define the next $\mathbb{Q}$ martingales:
\begin{align*} 
\bar{R}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R(t_0,t_1)  \right], \\
\bar{R}_{avg}(t,t_0,t_1) &:= \mathbb{E}_t^{\mathbb{Q}}\left[ R_{avg}(t_0,t_1)  \right].
\end{align*}
Before to continue, we will do several observations. The first observation is that if we define $F(t,t_0,t_1) = \mathbb{E}^{\mathbb{Q}^{t_1}}\left( R(t_0,t_1)\right)$, then we have that when $t \in [0,t_0]$
\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)}  \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
&= \frac{1}{\delta_{t_0,t_1}}\left(\frac{P_{ois}(t,t_0)}{P_{ois}(t,t_1)} - 1\right), %, \quad t \in [0,t_0] \\
%\end{align*}
\intertext{and when $t \in  [t_0, t_1]$, we have}
%\begin{align*}
F(t,t_0,t_1)&= \frac{1}{P_{ois}(t,t_1)} \mathbb{E}_{t}^{\mathbb{Q}}\left[\exp\left(-\int_{t}^{t_1} r_{ois,u} du \right) R(t_0,t_1) \right]\\
 &= \frac{1}{\delta_{t_0,t_1}} \left(\frac{\exp\left(\int_{t}^{t_1}r_{ois,u} du\right)}{P_{ois}(t_0,t)}-1\right).%, \quad  t \in  [t_0, t_1].
\end{align*}
Then the convexity adjustment for $ R(t_0,t_1)$ is
\begin{equation}\label{R_ois_ca}
CA_{ois}(t,t_0,t_1) = F(t,t_0,t_1) - \bar{R}(t,t_0,t_1).
\end{equation}
The second observation is that we have the following equivalence
\begin{equation}\label{R_ois_avg}
\mathbb{E}^{\mathbb{Q}}\left(R_{avg}(t_0,t_1) \right) =\frac{1}{\delta_{t_0,t_1}} \mathbb{E}^{\mathbb{Q}}\left[ \log\left(1+ \delta_{t_0,t_1} R(t_0,t_1) \right) \right]  \end{equation}
In order, to clarify the convexity expression and the calculations, we will define 
\begin{equation*}
I(t_0,t_1) := \int_{t_0}^{t_1} r_{ois,s} ds.
\end{equation*}

\begin{theorem}\label{Th_CA_OIS}[Convexity Adjustment approximation for OIS Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for OIS futures is 
\begin{equation}\label{convexity_ois_future}
\bar{R}(t_0,t_1) = \frac{1}{\delta_{t_0,t_1}}\left(\exp\left(\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right]\right)\exp\left(-\frac{1}{2}\int_{t}^{t_1}\Gamma^{2}(s,t_0,t_1) ds\right) - 1\right) + E(t_0),
\end{equation}
and for the average OIS future is
\begin{equation}\label{convexity_avg_ois_future}
\bar{R}_{avg}(t_0,t_1) = \frac{\mathbb{E}_t^{\mathbb{Q}}\left[I(t_0,t_1)\right] }{\delta_{t_0,t_1}} \approx \frac{1}{\delta_{t_0,t_1}}\left(\log\left(1+\delta_{t_0,t_1}  \mathbb{E}_t^{\mathbb{Q}}\left[R(t_0,t_1)\right] \right) - \frac{1}{2}\int_{0}^{t_1}  \Gamma^{2}(s,t_0,t_1) ds\right)
\end{equation}
where  
\begin{equation}
\Gamma(s,t_0,t_1)= \eta(s,x_0,y_0)\int_{\max(s, t_{0})}^{t_1} \exp\left( -\int_{s}^{u} k_{s^{\prime}} ds^{\prime}\right)du, 
\end{equation}
and $\|E(t_0)\|^{2}_{2} \sim \mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$.
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_OIS_futures}.
\end{proof}

@@

\begin{remark}
We can calculate the convexity adjustment for the case $t_0 < t < t_1$ similarly to when $t < t_0$. For this, we will define
\begin{align*}
I(t,t_1)&:=\int_{t}^{t_1} r_s ds,\\
R(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\frac{\exp\left(\int_{t}^{t_1} r_{ois,s} ds\right)}{P_{ois}(t_0,t)} - 1\right), \\
\intertext{and}
R_{avg}(t_0,t_1) &:= \frac{1}{\delta_{t_0,t_1}}\left(\int_{t_0}^{t} r_{ois,s} ds + \int_{t}^{t_1} r_{ois,s} ds\right).   
\end{align*}
\end{remark}

@@

\subsection{FRAs in arrears}
A FRA in arrears is the most classic example among the products with convexity adjustment. The price is given by 
\begin{equation}\label{FRAinArrear}
P_{E}(0,t_1)\mathbb{E}^{\mathbb{Q}^{t_1}}\left[L_{E}(t_1,t_1,t_2)\right],
\end{equation}
i.e. the cash flow associated to a FRA in arrears is $L_{E}(t_1,t_1,t_2)$ in $t_1$.

\begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for FRAs in Arrears is 
\begin{align}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) E(t_1) \nonumber \\
&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) (\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))) ds 
\end{align}
with $\|E(t_1)\|^{2}_{2} \sim \mathcal{O}(t_1) \quad \text{when} \quad t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty \quad \text{when} \quad t_1 \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_FRAsinArrears}.
\end{proof}

\begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
We can restrict the model the the Hull-White model with constant parameters. The analytical approximation that we get from \eqref{ca_approximations_fra_arrears} is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
\end{equation*}
In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$, $k=0.007$.
\begin{figure}[H]
		\begin{center}
		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
		\end{center}
		\caption{Convexity Mc Vs Convexity Malliavin}
		\label{fig:FRA_HW}
\end{figure}
\end{example}

@@

\begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypothesis \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Given
\begin{equation}
M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}
\end{equation}
Then, we have the temporal convexity adjustment for a CMS rate is approximated by
\begin{align} \label{cms_first_order_convexity}
CA(t_p) &\approx  E(t_a) + \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \nonumber \\
&\cdot \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds \nonumber 
\end{align}
with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_u du\right)\eta(u,x,y)$. And $\|E(t_a)\|^{2}_{2} \sim \mathcal{O}(t_a) \quad \text{when} \quad t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty \quad \text{when} \quad t_a \to \infty$
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_CMS}.
\end{proof}

@@

\subsection{Estimation of $\mathbb{E}_s^{\mathbb{Q}}\left[(x_t - \bar{x}_{t})^{2}\right]$}\label{estimation_error_l2}
In order to get the order of the approximation, we will use the ideas of the paper \cite{B-G-M-2008}. Basically, we will define a parametrization of the process $x_{t,\epsilon}$ and $y_{t,\epsilon}$ with $\epsilon \in [0,1]$. The role of $\epsilon$ is only as interpolation parameter between process. We will suppose the next parametrization of the Cheyette model

@@

The reason of $\epsilon^{2}$ in $y_{\epsilon,t}$ is because $\mathbb{E}^{\mathbb{Q}}\left[y_t\right]= \mathbb{V}ar(x_t)$. Then, if the scale of $x_{\epsilon,t}$ is $\epsilon$ then the scale of $y_{\epsilon,t}$ must be $\epsilon^{2}$. We will start with the estimation of $\mathbb{E}^{\mathbb{Q}}\left[(y_t - \bar{y}_t)^{2}\right]$. We will define the next parametrization for $\nu \in [0,1]$

@@

Then we have that $z^{1}_{u} = \eta(u,x_u,y_u)$ y $z^{0}_{u} = \eta(u,0,0)$. Therefore

@@

y_t = \bar{y}_t + E_{y}\left[t\right]

@@

\mathbb{E}^{\mathbb{Q}}\left[(E_{y}\left[t\right])^{2}\right] &\leq 4 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(-4 \int_{u}^{t} k(u^{\prime}) du^{\prime}\right)  \left(\int_{0}^{1} \eta(u, \nu x_u, \nu y_u)   \|\nabla_{x,y}\eta(u, \nu x_u, \nu y_u)\|^{2} \|(x_u, y_u)\| d\nu \right)^2 du \right] ^{2}\nonumber \\ 
&\leq 4 \|\eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_u, y_u)\|^{2}\right] du  \nonumber \\
&= M^{y}_k \int_{0}^{t} \mathbb{E}^{\mathbb{Q}}\left[\|(x_u, y_u)\|^{2}\right] du

@@

The next step is to estimate $\mathbb{E}^{\mathbb{Q}}\left[(x_t - \bar{x}_t)^{2}\right]$. From the definition of $x_t$, we have that

@@

x_t = \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \bar{y}_u du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}[u] du + \int_{0}^{t} \eta(t,x_u,y_u) dW_u. 

@@

In order, to find a expansion of $\eta(t,x_u,y_u)$ centered in $\bar{y}_u$, we will define $z^{\nu}_{u} = (1-\nu)\bar{y}_{u} + \nu y_u$. Then

@@

\eta(t,x_u,y_u) = \eta(t,x_u,\bar{y}_u) + \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu

@@

We will define $E_{x}(u) = \int_{0}^{1}\partial_y\eta(t,x_u,z^{\nu}_{u}) E_{y}[u] d\nu$. Then we have the next representation of $x_t$

@@

x_t = \bar{x}_t + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}[u] du + \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}[u] dW_u.

@@

 \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq \|\partial_y \eta \|^{2}_{\infty} \mathbb{E}^{\mathbb{Q}}[(E_{y}[u])^{2}]  

@@

 \mathbb{E}^{\mathbb{Q}}[(E_x[u])^{2}] \leq 4 \|\eta\|^{2}_{\infty} \|\partial_y \eta\|^{2}_{\infty} \max(\|\partial_x\eta\|^{2}_{\infty},\|\partial_y \eta\|^{2}_{\infty} ) \int_{0}^{u} \mathbb{E}^{\mathbb{Q}}\left[ \|(x_s, y_s)\|^{2}\right] ds

@@

\mathbb{E}^{\mathbb{Q}}[(x_t - \bar{x}_t)^{2}] & \leq 2 \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{y}(u) du    \right]^2\\
&+ \mathbb{E}^{\mathbb{Q}}\left[ \int_{0}^{t} \exp\left(- \int_{u}^{t} k(u^{\prime}) du^{\prime}\right) E_{x}(u) dW_u\right]^{2} \\
&\leq 2 \mathbb{E}^{\mathbb{Q}}\left[\int_{0}^{t} \exp\left(- 2\int_{u}^{t} k(u^{\prime}) du^{\prime}\right) \mathbb{E}^{\mathbb{Q}}(E^{2}_{y}(u)) du\right]\\
